Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

\begin{abstract}
This article addresses the dynamic properties of typical social networks. By
supposing that the evolution over time only includes creating new edges but no
deletion, we studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definitions are given to our metrics and
their mathematical analysis are put. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results could imply
that dynamic centrality is more capable in spotting hot social events.

@@

\section{Introduction}
Social networks is a surprising interdisciplinary field of social science and
computer science, allowing helpful analysis of large-scaled social behavior
and tendency. In this paper, we will deal with more information of social
networks, the time dimension, and make a similar study to the social behaviors.
We build metrics for evolving social networks and design an algorithm to
calculate them. We compare how different the outcome by our method would be
against the classical analysis with un-timestamped data mining.

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph.  The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but refer to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some kind of graph centralities. However, most
social networks change over time, and even more unfortunately, many of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancement the speed of answering consistent
querying.

In section 3 we will concentrate on centrality and activity in evolving social
network. We will define what centrality or activity is good, and we will design
some instance of those metrics by the standard we set. In section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In section 5, we will show the metrics make
sense with real world data.

\subsection{Algorithms}
Graph theory is very successful on storing and solving various problems on
static networks, we have sophisticated methodology on finding the shortest
paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
And we also have a well-established theoretical system to study problems that
do not seems to have perfect solutions. However, dynamic online queries can be
very hard for general graphs. Best known solutions for many dynamic basic graph
problems still remain unsatisfiable for general demands. So to design metrics
for an general evolving network is a very challenging and open problem. We
concentrate on the popular studied social networks and try to create meaningful
and available approaches of operation on such networks.

>>>>

\begin{abstract}
This article addresses the dynamic properties of typical social networks. By
supposing that the evolution over time only includes creating new edges but no
deletion, we studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definitions are given to our metrics and
their mathematical analysis are put. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results imply
that dynamic centrality is more capable in spotting hot social events.

@@

\section{Introduction}
Social networks is a surprising interdisciplinary field of social science and
computer science, allowing helpful analysis of large-scaled social behavior
and tendency. In this article, we are able to deal with more information, the
time dimension, of social networks, and make a similar study to the social
behaviors.  We build metrics for evolving social networks and design an
algorithm to calculate them. We compare out results with the classical analysis
which works under un-timestamped data.

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploit the basic form of
quantification to concentrate on specific features of the whole graph or an
individual vertex. Our work is to extend this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph. The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but refer to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some kind of graph centralities. However, most
social networks change over time, and even more unfortunately, many of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limiting the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancing the speed of answering consistent
querying.

In section 3 we will concentrate on centrality and activity in evolving social
network. We will define what kind of activity is good, and we will design
an instance of those metrics by the standard we set. In section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In section 5, we will show the metrics make
sense with real world data.

\subsection{Algorithms}
Graph theory is very successful on storing and solving various problems on
static networks. We have sophisticated method on finding the shortest
paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
And we also have a well-established theoretical system to study problems that
do not seems to have perfect solutions. However, dynamic online queries can be
very hard for general graphs. Best known solutions for many dynamic basic graph
problems still remain unsatisfiable for general demands. So to design metrics
for an general evolving network is a very challenging and open problem. We
concentrate on the popular studied social networks and try to create meaningful
and available approaches of operation on such networks.
